Bayesian Evidence Synthesis:Opioid Crisis

### 2020-04-27 latex/researchpaper.tex
I am dying

\begin{figure}[htb]
	\centering
	\includegraphics[width=200mm,scale=0.5]{Figures/simple_drawing}
	\caption{Example of estimating the total number of overdoses indirectly given two data sets: ambulance attended overdoses and survey data.}
	\label{simple_draw}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/earlyresult1_ot.png}
	\caption{Boxplot of posterior samples of $O_t$ (2000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/hist_sum_ot.png}
	\caption{Histogram of posterior samples of total overdoses per year}
	\label{hst_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $O_t$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-o_t.png}\label{under_ot}}
	\subfloat[ppc of $O_t$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-o_t}\label{over_ot}}
	\caption[Initial result: box plot of posterior samples of $O_t$ ]{Boxplot of posterior samples of $O_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $O_t$ values are shown as red dots.}
	\label{contam_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-u_t.png}\label{under_ut}}
	\subfloat[ppc of $U_t$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-u_t}\label{over_ut}}
	\caption[Initial result: boxplot of posterior samples of $U_t$]{Box plot of posterior samples of $U_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $U_t$ values are shown as red dots.}
	\label{contam_ut}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat[ppc of $x_{A,t}$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-x_a.png}\label{under_xa}}
	\subfloat[ppc of $x_{A,t}$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-x_a.png}\label{over_xa}}
	\caption[Initial result: b	oxplot of posterior samples of $x_{A,t}$]{Boxplot of posterior samples of $x_{A,t}$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $x_{A,t}$ values are shown as red dots.}
	\label{contam_xt}
\end{figure}

@@

where the prior information suggests that $N$ is most likely around 10000 and $\pm 20\%$ of the point estimation covers  95\% of the symmetric support of $N$.
\subsubsection{Posterior Distribution}
Both MCMC algorithms from pyMC3 and JAGS suffered from relatievely long running time of the algorithms and the convergence issue of the trace of $N$. From the trace plot of $N$, two chains of the variable covered a common distribution but neither sequence appeared stationary after 10000000 iterations and the effective sample size for N was 56271. Figure \ref{trace_N} shows the trace plot and the posterior density plot of N. It is shown that the two chains cross over each other multiple times but they do not seem stationary even with 10000000 iterations. The posterior distribution seems to be roughly symmetric at the center 10000. 
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/not_mixed_N.png}
	\caption{Trace plot of $N$}
	\label{trace_N}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/hist_N.png}
	\caption{Boxplot of posterior samples of $N$ (20000 samples for each month)}
	\label{hist_unk_n}
\end{figure}

Posterior samples of $O_t$ was accurate as before. [mention that although the mixing was not possible with the maximum capacity of the computer, at least the proper prior seems to help a lot for the estimation of $O_t$ which depends on the N. ][put the figure and briefly explain that the the estimation for the variable is not hugely affected.]
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/unknown_N_ot.png}
	\caption{Boxplot of posterior samples of $O_t$ (20000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot_unk_n}
\end{figure}

@@

[put the figures and briefly explain that the the estimation for the variables are not hugely affected.]
\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$]{\includegraphics[width=.50\columnwidth]{Figures/unk_N_ppc1_ut.png}\label{ppc_ut_unk_n}}
	\subfloat[ppc of $x_{A,t}$]{\includegraphics[width=.50\columnwidth]{unk_N_ppc1_xt}\label{ppc_xt_unk_n}}
	\caption[Initial result: box plots of predictive posterior samples of $U_t$ and $x_{A,t}$]{Boxplots of posterior predictive samples of $U_t$ and $x_{A,t}$ (1000 samples) with the actual data point of simulated $U_t$,$x_{A,t}$ value. The simulated values are shown as a red dots.}

>>>>

\begin{figure}[htb]
	\centering
	\includegraphics[width=200mm,scale=0.5]{Figures/simple_drawing}
	\caption[Example of estimating the total number of overdoses]{Example of estimating the total number of overdoses indirectly given two data sets: ambulance attended overdoses and survey data.}
	\label{simple_draw}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/earlyresult1_ot.png}
	\caption[Initial result: boxplot of posterior samples of $O_t$]{Boxplot of posterior samples of $O_t$ (2000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/hist_sum_ot.png}
	\caption[Initial result: histogram of posterior samples of total overdoses per year]{Histogram of posterior samples of total overdoses per year}
	\label{hst_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $O_t$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-o_t.png}\label{under_ot}}
	\subfloat[ppc of $O_t$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-o_t}\label{over_ot}}
	\caption[Contaminated $p_{A,t}$: boxplot of posterior samples of $O_t$ ]{Boxplot of posterior samples of $O_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $O_t$ values are shown as red dots.}
	\label{contam_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-u_t.png}\label{under_ut}}
	\subfloat[ppc of $U_t$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-u_t}\label{over_ut}}
	\caption[Contaminated $p_{A,t}$: boxplot of posterior samples of $U_t$]{Box plot of posterior samples of $U_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $U_t$ values are shown as red dots.}
	\label{contam_ut}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat[ppc of $x_{A,t}$: underestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-x_a.png}\label{under_xa}}
	\subfloat[ppc of $x_{A,t}$: overestimated $p_{A,t}$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-x_a.png}\label{over_xa}}
	\caption[Contaminated $p_{A,t}$:: boxplot of posterior samples of $x_{A,t}$]{Boxplot of posterior samples of $x_{A,t}$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $x_{A,t}$ values are shown as red dots.}
	\label{contam_xt}
\end{figure}

@@

where the prior information suggests that $N$ is most likely around 10000 and $\pm 20\%$ of the point estimation covers  95\% of the symmetric support of $N$.
\subsubsection{Posterior Distribution}
Both MCMC algorithms from pyMC3 and JAGS suffered from relatievely long running time of the algorithms and the convergence issue of the trace of $N$. From the trace plot of $N$, two chains of the variable covered a common distribution but neither sequence appeared stationary after 10000000 iterations and the effective sample size for N was 56271. Figure \ref{trace_N} shows the trace plot and the posterior density plot of N. It is shown that the two chains cross over each other multiple times but they do not seem stationary even with 10000000 iterations. The posterior distribution seems to be roughly symmetric at the center 10000. 
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/not_mixed_N.png}
	\caption[Unobserved $N$: trace plot of latent variable $N$]{Trace plot of latent variable $N$}
	\label{trace_N}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{Figures/hist_N.png}
	\caption[Unobserved $N$: boxplot of posterior samples of $N$]{Boxplot of posterior samples of $N$ (20000 samples for each month)}
	\label{hist_unk_n}
\end{figure}

Posterior samples of $O_t$ was accurate as before. [mention that although the mixing was not possible with the maximum capacity of the computer, at least the proper prior seems to help a lot for the estimation of $O_t$ which depends on the N. ][put the figure and briefly explain that the the estimation for the variable is not hugely affected.]
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/unknown_N_ot.png}

	\caption[Unobserved $N$: boxplot of posterior samples of $O_t$]{Boxplot of posterior samples of $O_t$ (20000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot_unk_n}
\end{figure}

@@

[put the figures and briefly explain that the the estimation for the variables are not hugely affected.]
\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$]{\includegraphics[width=.50\columnwidth]{Figures/unk_N_ppc1_ut.png}\label{ppc_ut_unk_n}}
	\subfloat[ppc of $x_{A,t}$]{\includegraphics[width=.50\columnwidth]{unk_N_ppc1_xt}\label{ppc_xt_unk_n}}
	\caption[Unobserved $N$: box plots of predictive posterior samples of $U_t$ and $x_{A,t}$]{Boxplots of posterior predictive samples of $U_t$ and $x_{A,t}$ (1000 samples each) with the actual data point of simulated $U_t$, $x_{A,t}$ value. The simulated values are shown as a red dots.}
